Plug-and-play dual-tree algorithm runtime analysis

### 2015-10-07 bounds-files/imbalance.tex
Note that c ~ O(N) in the footnote.

An imbalanced cover tree can happen in practice, and in the worst cases, the
imbalance may be far worse than the simple graphs of Figure \ref{fig:imbalance}.
Consider a dataset with a single outlier which is very far away from all of the
other points\footnote{Note also that for an outlier sufficiently far away, the
expansion constant is $N - 1$, so we should expect poor performance with the
cover tree anyway.}.  Figure \ref{fig:outlier} shows what happens in
this situation: the root node has two children; one of these children has only
the outlier as a descendant, and the other child has the rest of the points in
the dataset as a descendant.  In fact, it is easy to find datasets with a
handful of outliers that give rise to a chain-like structure at the top of the
tree: see Figure \ref{fig:outliers} for an illustration\footnote{As a side note,
this behavior is not limited to cover trees, and can happen to mean-split
$kd$-trees too, especially in higher dimensions.}.

>>>>

An imbalanced cover tree can happen in practice, and in the worst cases, the
imbalance may be far worse than the simple graphs of Figure \ref{fig:imbalance}.
Consider a dataset with a single outlier which is very far away from all of the
other points\footnote{Note also that for an outlier sufficiently far away, the
expansion constant is $N - 1$, so we should expect poor performance with the
cover tree anyway.}.  Figure \ref{fig:outlier} shows what happens in
this situation: the root node has two children; one of these children has only
the outlier as a descendant, and the other child has the rest of the points in
the dataset as a descendant.  In fact, it is easy to find datasets with a
handful of outliers that give rise to a chain-like structure at the top of the
tree: see Figure \ref{fig:outliers} for an illustration\footnote{As a side note,
this behavior is not limited to cover trees, and can happen to mean-split
$kd$-trees too, especially in higher dimensions.  In addition, for this
scenario to arise with cover trees, it must be true that $c \sim O(N)$.}.
